---
title: "CV"
format:
  html:
    toc: true
    toc-depth: 2
---

```{r}
#| echo: false
#| message: false
source("R/cv_helpers.R")
cv <- yaml::read_yaml("_data/cv_data.yml")

# NOTE: glue::glue() trims trailing whitespace/newlines from its result
# by default, so a trailing "\n" *inside* a glue template gets silently
# dropped. We build each entry as a line with no trailing \n, then join
# all lines for a section with "\n\n" and cat() the whole thing ONCE --
# multiple separate cat() calls in a loop also aren't reliably a
# newline apart once knitr collects the asis output, so one final
# string is the safe way to get real paragraph breaks between entries.

fmt_block <- function(entries) {
  lines <- vapply(entries, function(e) {
    place <- if (nzchar(e$place %||% "")) glue::glue(" — {e$place}") else ""
    line <- glue::glue("**{e$dates}** · {e$title}{place}")
    if (nzchar(e$detail %||% "")) line <- glue::glue("{line}  \n{e$detail}")
    as.character(line)
  }, character(1))
  cat(paste(lines, collapse = "\n\n"), "\n")
}

fmt_collection <- function(df) {
  if (nrow(df) == 0) { cat("_Nothing here yet._\n"); return(invisible()) }
  lines <- vapply(seq_len(nrow(df)), function(i) {
    d <- format_cv_date(df$date[i])
    sub <- if (nzchar(df$subtitle[i])) glue::glue(" — {df$subtitle[i]}") else ""
    line <- glue::glue("**{d}** · {df$title[i]}{sub}")
    if (nzchar(df$body[i])) line <- glue::glue("{line}  \n{df$body[i]}")
    as.character(line)
  }, character(1))
  cat(paste(lines, collapse = "\n\n"), "\n")
}
```

A shorter, browsable version of my CV. For the full formatted document, [download the PDF ↓](assets/cv.pdf) — it's generated automatically from the same source files as this page.

## Education

```{r}
#| echo: false
#| output: asis
fmt_block(cv$education)
```

## Academic positions

```{r}
#| echo: false
#| output: asis
fmt_block(cv$positions)
```

## Publications

```{r}
#| echo: false
#| output: asis
fmt_collection(read_collection("publications"))
```

## Invited talks

```{r}
#| echo: false
#| output: asis
talks <- read_collection("talks")
fmt_collection(talks[has_category(talks$categories, "Invited talk"), ])
```

## Presentations

```{r}
#| echo: false
#| output: asis
fmt_collection(talks[!has_category(talks$categories, "Invited talk"), ])
```

## Teaching

```{r}
#| echo: false
#| output: asis
fmt_collection(read_collection("teaching"))
```

## Awards

```{r}
#| echo: false
#| output: asis
fmt_block(cv$awards)
```

## Grants

```{r}
#| echo: false
#| output: asis
fmt_block(cv$grants)
```

## Skills

**IT** — Advanced: `r paste(cv$skills$it_advanced, collapse = ", ")`. Intermediate: `r paste(cv$skills$it_intermediate, collapse = ", ")`.

```{r}
#| echo: false
#| output: asis
lines <- vapply(cv$skills$languages, function(l) glue::glue("- **{l$language}**: {l$level}"), character(1))
cat(paste(lines, collapse = "\n"), "\n")
```

## Additional training

```{r}
#| echo: false
#| output: asis
fmt_block(cv$training)
```

## Scientific affiliations

```{r}
#| echo: false
#| output: asis
cat(paste(unlist(cv$affiliations), collapse = ", "))
```

## References

```{r}
#| echo: false
#| output: asis
lines <- vapply(cv$references, function(r) {
  glue::glue("- **{r$name}** — {r$place} — [{r$email}](mailto:{r$email})")
}, character(1))
cat(paste(lines, collapse = "\n"), "\n")
```
